% -------------------------------------------------
% Yue Fei — One-page Resume (XeLaTeX)
% -------------------------------------------------

\documentclass[letterpaper,10pt]{article}

% ---------- Layout ----------
\usepackage[top=1cm, bottom=2cm, left=1.3cm, right=2cm]{geometry}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{fontawesome5}
\usepackage{hyperref}

% ---------- Theme ----------
\usepackage{friggeri_sourabh_theme}

% ---------- Global spacing ----------
\setstretch{0.96}
\raggedright
\setlength{\parindent}{0pt}
\setlist[itemize]{itemsep=1pt, topsep=0pt, parsep=0pt}

% ---------- Custom lengths ----------
\newlength\DateCol
\setlength\DateCol{3.7cm}

% ---------- Headings ----------
\newcommand{\eduHeading}[3]{%
  \renewcommand{\arraystretch}{1.1}
  \begin{tabularx}{\linewidth}{@{}X >{\raggedleft\arraybackslash}p{\DateCol}@{}}
    \textbf{#1} & \textit{#3} \\
    \textit{#2} & \\
  \end{tabularx}
}

\newcommand{\jobHeading}[4]{%
  \renewcommand{\arraystretch}{1.05}
  \begin{tabularx}{\linewidth}{@{}X >{\raggedleft\arraybackslash}p{\DateCol}@{}}
    \textbf{#1}%
    {\footnotesize\color{secondary_body}\hspace{0.4em}· #3} &
    \makebox[\DateCol][r]{\textit{#4}} \\
    \textit{#2} & \\
  \end{tabularx}
}

\newcommand{\projHeading}[2]{%
  \renewcommand{\arraystretch}{1.15}%
  \begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}X >{\raggedleft\arraybackslash}p{\DateCol}@{}}%
    {\textbf{#1}} &
    \makebox[\DateCol][r]{\textit{#2}} \\
  \end{tabularx}%
}


\newcommand{\itemListStart}{\begin{itemize}}
\newcommand{\itemListEnd}{\end{itemize}\vspace{1pt}}
\newcommand{\myItem}[1]{\item #1}

% ---------- Document ----------
\begin{document}

% ---------- HEADER ----------
\makecvheader

\noindent{\color{lightgray}\rule{\textwidth}{0.4pt}}
\vspace{-14pt}


% ---------- Education ----------
\cvsection{Education}
\eduHeading
  {University of Toronto}
  {Master of Engineering, Electrical \& Computer Engineering}
  {Sep.~2022 -- Jun.~2024}
\itemListStart
  \myItem{%
    \thesistitle{\textbf{MEng Thesis (Individual):} \emph{Pilot Training -- Angle of Arrival and Channel Estimation in 5G Network}}
    \ \href{https://github.com/fireflyndmoon43/UMa_5G_AoA}{\textcolor{NavySecondary}{\textbf{[Code]}}}
  }

  \myItem{Compared \textbf{Linear Minimum Mean Square Error (LMMSE)} approach and \textbf{Matrix-Pencil Method (MPM)} for uplink channel estimation in \textbf{multicell MIMO-OFDM systems} with four distributed units (DUs) arranged in a square of radius 100 m, using a 3GPP-compliant MATLAB model.}
  \myItem{Showed that with \textbf{pilot training} in time or frequency domain, MPM yields higher angle-of-arrival accuracy than DFT-based and MMSE methods with limited antennas.}
  \myItem{Supervisor: \advisorlink{https://www.comm.utoronto.ca/~rsadve/}{Prof.~Raviraj Adve}}
\itemListEnd

\eduHeading
  {University of Toronto}
  {Bachelor of Applied Science, Electrical Engineering}
  {Sep.~2017 -- Jun.~2022}
\itemListStart
  \myItem{%
    \thesistitle{\textbf{Capstone Project (Teamwork):} \emph{CNN NPU Overlay (MobileNetV1) on Intel Stratix~10~NX}}
  }
  \myItem{Collaborated to replace the original matrix–vector unit of the Microsoft Brainwave NPU on Intel Stratix 10 NX with a \textbf{custom convolution unit (scheduler + tiles + accumulator)}, achieving \textbf{4.3×} speedup and \textbf{76.6 GOP/s} on MobileNetV1 inference.}
  \myItem{Collaborate to develop a \textbf{VLIW-based Python compiler} and \textbf{ISA simulator} to translate Keras models into NPU instructions, managing memory allocation and cycle-accurate performance verification.}
  \myItem{Designed a \textbf{pipelined accumulator} enabling 330 MHz operation; implemented three-stage \textbf{reduction-tree addition} and \textbf{opcode-based accumulation modes}, verified correct synchronization and 450 MHz Fmax in Quartus.}
  \myItem{Supervisors:
  \advisorlink{https://www.eecg.utoronto.ca/~vaughn/}{Prof.~Vaughn Betz},
  \advisorlink{https://andrewboutros.github.io/}{Andrew Boutros}}
\itemListEnd

% ---------- Publications ----------
\cvsectionwithmeta{Publications}{Peer-reviewed conferences}
\vspace{-2pt}
\pubListStart
\item Arash Ahmadian, Louis S.P. Liu, \textbf{Yue Fei}, Konstantinos N. Plataniotis, Mahdi S. Hosseini. \href{https://ieeexplore.ieee.org/document/10097215/}{\papertitle{Pseudo-Inverted Bottleneck Convolution for DARTS Search Space}}.
\conference{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}, 2023.

\item Abnash Bassi, \textbf{Yue Fei}, Gilead Posluns, Mark C. Jeffrey.
\papertitle{Optimized Priority Scheduling for Faster Scalable Belief Propagation}.
\conference{Probabilistic Graphical Models (PGM)}, \submissionstatus{In Submission}, 2026.
\pubListEnd


% ---------- Experience ----------
\cvsection{Experience}
\jobHeading
  {MediumAI}
  {Software Development Engineer — Hybrid, Toronto, Canada}
  {Freelance}
  {Jan.~2026 -- Present}
\itemListStart
  \myItem{Build API integrations for a voice LLM–powered medical scribe agent, enabling secure multilingual clinical documentation.}
\itemListEnd

\jobHeading
  {iQIYI.com}
  {Data Analyst — Remote, Beijing, China}
  {Internship}
  {Oct.~2025 -- Dec.~2025}
\itemListStart
  \myItem{Combined three-arm A/B testing with causal forests and decision-tree rules for deployable personalization, lifting renewal rates from \textbf{37\%} to \textbf{54.06\%.}}
\itemListEnd

\jobHeading
  {Qualcomm Canada}
  {RFIC Design Verification Engineer — Onsite, Markham, Canada}
  {Permanent Full-time}
  {Jun.~2024 -- Jul.~2025}
\itemListStart
  \myItem{Verified UWB receiver path(analog front end); improved UWB receiver bootup by reducing LNA charging delay \textbf{90\%} (20\,ns$\rightarrow$2\,ns); Verified WLAN CP-PLL synthesizer across 500+ channels using UVM, ensuring coverage over 2G/5G bands.}
  \myItem{Developed GRU-based multi-head model for analog gain line-up optimization and an MLP for VCO capacitance prediction, replacing manual tuning across 1000+ frequency targets.}
\itemListEnd

\jobHeading
  {University of Toronto -- WIRLab}
  {Research Assistant — Remote, Toronto, Canada}
  {Contract Part-time}
  {Jul. 2021 -- Sep. 2021}
\itemListStart
  \myItem{Explored \textbf{RNN-based Transformer models} and \textbf{Attention mechanisms} for NLP tasks.}\href{https://github.com/fireflyndmoon43/attn_nmt_visualize/blob/main/Final_Report_2021_08_30.pdf}{\textcolor{NavySecondary}{\textbf{[Code]}}}
  \myItem{Applied \textbf{PCA-based embedding visualization}—as used in \textbf{GloVe}—to project high-dimensional embeddings into \textbf{2D/3D space} using \textbf{Python (NumPy, Matplotlib)}, enabling intuitive inspection of semantic clusters.}
\itemListEnd


\jobHeading
  {Alphawave Semi}
  {SerDes Digital Verification Engineer — Remote, Toronto, Canada}
  {Internship}
  {May~2020 -- Jun.~2021}
\itemListStart
  \myItem{Built UVM testbenches for SerDes subsystems (clocking, datapath, SRAM), expanding coverage to 50+ scenarios; Scaled Jenkins CI/CD regression from 4 to 60+ projects, enabling \textbf{15$\times$} throughput growth.}
\itemListEnd

% ---------- Awards ----------
\cvsection{Awards and Certificates}
\itemListStart
\vspace{-4pt}
\item Edward S. Rogers Sr. Department Betz Entrance Scholarship (\$5,000) \hfill \textit{2017}
\item Certificate in Engineering Business  \hfill \textit{Jun. 2022}
\itemListEnd

\cvsection{Invited Talks}
\vspace{-2pt}
\talkItem
  {Qualcomm Panel Discussion: \textit{Demystifying Machine Learning}}
  {Talk: \textit{From Channels to States — Machine Learning in the Language of Communication and Control}}
  {QWomen San Diego}
  {Mar.\ 2025}

% ---------- Projects ----------
\cvsection{Selected Academic Projects}
\vspace{-4pt}
\projCategory{Computer Architecture \& Systems}
\projHeading{Parallel Beamforming \& Cache-Coherence}{Jan.~2024 -- May.~2024}
\itemListStart
  \myItem{Accelerated medical imaging by \textbf{7×} (17\,s $\rightarrow$ 2.5\,s) via \textbf{16-thread data-parallel} ultrasound beamforming with Intel SIMD intrinsics and memory optimizations (\texttt{restrict}); validated correctness (RMS error $<10^{-16}$) and scalability (1–16 threads).}
  \href{https://github.com/fireflyndmoon43/ece1755/blob/main/assignment1_code/beamform_mt.c}{\textcolor{NavySecondary}{\textbf{[Code]}}}
  \myItem{Designed and verified a \textbf{3-hop directory cache-coherence protocol} (MSI/MESI) in Mur$\phi$, optimizing with an \textbf{Exclusive (E)} state to eliminate unnecessary bus transactions.}
  \href{https://github.com/fireflyndmoon43/Murphi3.1-CacheCoherence/tree/main/ece1755_sample}{\textcolor{NavySecondary}{\textbf{[Code]}}}
\itemListEnd

\projHeading{Computer Architecture Coursework (Team of 2)}{Sep.~2021 -- Dec.~2021}
\itemListStart
  \myItem{Modeled \textbf{data hazard detection} in a modified \textbf{MIPS 6-stage pipelined CPU}, validating correctness via explicit stall-cycle annotation.}
  \myItem{Designed a \textbf{perceptron-based branch predictor}, combining local branch history with long global history to reduce MPKI under tight storage constraints.}
  \myItem{Implemented \textbf{Tomasulo out-of-order execution} with register renaming and dynamic scheduling, and an \textbf{MSI directory-based cache-coherence protocol}.}
  \myItem{Implemented a \textbf{Bouquet L1 data prefetcher} using IPCP, DPT, and a global history buffer (GHB) with confidence-based arbitration.}
  \mySubItem{Evaluated feasibility using CACTI, showing \textbf{$\sim$24\%} area overhead and parallel access within \textbf{$<1$\,ns} latency.}
\itemListEnd

\projCategory{Error-Correcting Codes \& Graphical Inference}

\projHeading{Graph-Based Error-Correcting Codes}{Sep.~2023 -- Dec.~2023}
\itemListStart
  \myItem{Implemented \textbf{LDPC}, fountain/LT, and \textbf{Polar encoders/decoders} over the binary-erasure channel, developing custom simulators in Julia and MATLAB.}
  \href{https://github.com/fireflyndmoon43/ECE1508-Graphs-Codes-and-Inference}{\textcolor{NavySecondary}{\textbf{[Code]}}}
\itemListEnd

\projHeading{Error Control Coding: Convolutional \& BCH Codes}{Jan.~2023 -- May.~2023}
\itemListStart
  \myItem{Implemented \textbf{convolutional encoders} with \textbf{Viterbi decoding} and \textbf{binary BCH encoders/decoders} over \(GF(2^m)\) using custom trellis structures in MATLAB.}
\itemListEnd

\projCategory{Information Theory \& Semantic Communications}

\projHeading{Sampling-Based Semantic Source Coding (One-Shot Information Theory)}{Jan.~2023 -- May.~2023}
\itemListStart
  \myItem{Implemented \textbf{Poisson functional representation}, \textbf{rejection sampling}, \textbf{importance sampling}, and hybrid Poisson\,+\,dithered quantization for 6G semantic source coding in MATLAB.}
  \href{https://github.com/fireflyndmoon43/ECE1508-OneShotInfoTheory/tree/main}{\textcolor{NavySecondary}{\textbf{[Code]}}}
\itemListEnd

\projCategory{Wireless Communications \& Signal Processing}

\projHeading{LTE Signal Processing}{Jan.~2022 -- Apr.~2022}
\itemListStart
  \myItem{Processed captured LTE signals for \textbf{time/frequency synchronization}, \textbf{OFDM demodulation}, and \textbf{channel equalization}; resampled 40\,MHz RF data to the 30.72\,MHz LTE rate and validated \textbf{PSS/SSS} detection.}
\itemListEnd



\end{document}
