% -------------------------------------------------
% Yue Fei — One-page Resume (XeLaTeX)
% -------------------------------------------------

\documentclass[letterpaper,10pt]{article}

% ---------- Layout ----------
\usepackage[top=1cm, bottom=1.2cm, left=1.3cm, right=1cm]{geometry}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{fontawesome5}
\usepackage{hyperref}

% ---------- Theme ----------
\usepackage{friggeri_sourabh_theme}
\pagenumbering{gobble} 
% ---------- Global spacing ----------
\setstretch{0.96}
\raggedright
\setlength{\parindent}{0pt}
\setlist[itemize]{itemsep=1pt, topsep=0pt, parsep=0pt}

% ---------- Custom lengths ----------
\newlength\DateCol
\setlength\DateCol{3.7cm}

% ---------- Headings ----------
\newcommand{\eduHeading}[3]{%
  \renewcommand{\arraystretch}{1.1}
  \begin{tabularx}{\linewidth}{@{}X >{\raggedleft\arraybackslash}p{\DateCol}@{}}
    \textbf{#1} & \textit{#3} \\
    \textit{#2} & \\
  \end{tabularx}
}

\newcommand{\jobHeading}[4]{%
  \renewcommand{\arraystretch}{1.0}
  \begin{tabularx}{\linewidth}{@{}X >{\raggedleft\arraybackslash}p{\DateCol}@{}}
    \textbf{\color{primary}#1} {\small\hspace{0.5em}· \textbf{\color{accent_body}#2} · \color{secondary_body}#3} & \textit{#4} \\
  \end{tabularx}
}


\newcommand{\projHeading}[2]{%
  \renewcommand{\arraystretch}{1.15}%
  \begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}X >{\raggedleft\arraybackslash}p{\DateCol}@{}}%
    {\textbf{\color{primary}#1}} &
    \makebox[\DateCol][r]{\textit{#2}} \\
  \end{tabularx}%
}


\newcommand{\itemListStart}{\begin{itemize}}
\newcommand{\itemListEnd}{\end{itemize}\vspace{1pt}}
\newcommand{\myItem}[1]{\item #1}

% ---------- Document ----------
\begin{document}

% ---------- HEADER ----------
\makecvheader

\noindent{\color{lightgray}\rule{\textwidth}{0.4pt}}
\vspace{-14pt}

% ---------- Experience ----------
\cvsection{Experience}
\jobHeading
  {MediumAI}
  {Software Development Engineer — Hybrid, Toronto, Canada}
  {Freelance}
  {Jan.~2026 -- Present}
\itemListStart
  \myItem{Build API integrations for a voice-LLM powered medical scribe agent, enabling secure multilingual clinical records.}
\itemListEnd

\jobHeading
  {iQIYI.com}
  {Data Analyst — Remote, Beijing, China}
  {Internship}
  {Oct.~2025 -- Dec.~2025}
\itemListStart
  \myItem{Combined three-arm A/B testing with causal forests and decision-tree rules for deployable personalization, lifting renewal rates from \textbf{37\%} to \textbf{54.06\%.}}
\itemListEnd

\jobHeading
  {Qualcomm Canada}
  {RFIC Design Verification Engineer — Onsite, Markham, Canada}
  {Permanent Full-time}
  {Jun.~2024 -- Jul.~2025}
\itemListStart
  \myItem{Verified UWB RX analog front-end and WLAN CP-PLL across 500+ channels using UVM; built GRU/MLP models for analog gain and VCO tuning, replacing manual calibration across 1000+ targets.}
\itemListEnd


\jobHeading
  {University of Toronto -- WIRLab}
  {Research Assistant — Remote, Toronto, Canada}
  {Contract Part-time}
  {Jul. 2021 -- Sep. 2021}
\itemListStart
  \myItem{Applied PCA-based embedding visualization to investigate semantic clusters for \textbf{Transformer-based NLP tasks}.}\href{https://github.com/fireflyndmoon43/attn_nmt_visualize/blob/main/Final_Report_2021_08_30.pdf}{\textcolor{NavySecondary}{\textbf{[Code]}}}
\itemListEnd


\jobHeading
  {Alphawave Semi}
  {SerDes Digital Verification Engineer — Remote, Toronto, Canada}
  {Internship}
  {May~2020 -- Jun.~2021}
\itemListStart
  \myItem{Built UVM testbenches for SerDes subsystems (clocking, datapath, SRAM), expanding coverage to 50+ scenarios; Scaled Jenkins CI/CD regression from 4 to 60+ projects, enabling \textbf{15$\times$} throughput growth.}
\itemListEnd

% ---------- Education ----------
\cvsection{Education}
\eduHeading
  {University of Toronto}
  {Bachelor of Applied Science, Electrical Engineering}
  {Sep.~2017 -- Jun.~2022}
\itemListStart
\myItem{%
\textbf{Capstone:} CNN NPU overlay + compiler for Intel Stratix~10~NX;
custom CONVU + DLS compiler for MobileNetV1, achieving \textbf{4.3×} speedup over Brainwave.
\textit{Supervisors: Prof.~Vaughn Betz, Andrew Boutros}.}
\itemListEnd


\eduHeading
  {University of Toronto}
  {Master of Engineering, Electrical \& Computer Engineering}
  {Sep.~2022 -- Jun.~2024}
\itemListStart
\myItem{%
\textbf{MEng Thesis:} \emph{Pilot Training for AoA and Channel Estimation in 5G MIMO-OFDM};
evaluated \textbf{LMMSE vs.\ Matrix-Pencil} methods under 3GPP-compliant multicell models,
showing \textbf{higher AoA accuracy} with limited antennas.
\textit{Supervisor: Prof.~Raviraj Adve}.}
\itemListEnd

% ---------- Publications ----------
\cvsectionwithmeta{Publications}{Peer-reviewed conferences}
\vspace{-2pt}
\pubListStart
\item Arash Ahmadian, Louis S.P. Liu, \textbf{Yue Fei}, Konstantinos N. Plataniotis, Mahdi S. Hosseini. \href{https://ieeexplore.ieee.org/document/10097215/}{\papertitle{Pseudo-Inverted Bottleneck Convolution for DARTS Search Space}}.
\conference{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}, 2023.

\item Abnash Bassi, \textbf{Yue Fei}, Gilead Posluns, Mark C. Jeffrey.
\papertitle{Optimized Priority Scheduling for Faster Scalable Belief Propagation}.
\conference{Probabilistic Graphical Models (PGM)}, \submissionstatus{In Submission}, 2026.
\pubListEnd

% ---------- Projects ----------
\cvsection{Selected Academic Projects}
\vspace{-4pt}

\projCategory{Computer Architecture \& Digital Design Systems}

\itemListStart
\small{
\myItem{\textbf{Parallel Beamforming \& Cache Coherence (ECE1755):}
Accelerated ultrasound beamforming by \textbf{7×} (17\,s$\rightarrow$2.5\,s) using \textbf{16-thread SIMD parallelism} and memory optimizations (\texttt{restrict});
designed and verified a \textbf{3-hop MSI/MESI directory protocol} in Mur$\phi$ with an \textbf{Exclusive (E)} state to reduce bus traffic.
\href{https://github.com/fireflyndmoon43/ece1755}{\textcolor{NavySecondary}{\textbf{[Code]}}}
}

\myItem{\textbf{Parallel Graph Inference Scheduler (ECE1755 Project):}
Built a multi-threaded asynchronous scheduler for \textbf{LDPC, Ising, and Potts} models using a \textbf{Stealing Multi-Queue (SMQ)};
optimized sparse graph traversal via \textbf{CSR layouts}, improving cache efficiency on \textbf{48-thread} manycore systems.}

\myItem{\textbf{Computer Architecture (ECE552):}
Implemented \textbf{MIPS 6-stage pipelined CPU} with hazard detection, \textbf{Tomasulo OoO execution},
\textbf{perceptron branch prediction}, MSI directory coherence, and a \textbf{Bouquet L1 prefetcher} (IPCP+DPT+GHB);
evaluated area/latency tradeoffs using CACTI (\textbf{$\sim$24\%} area, $<1$\,ns access).}

\myItem{\textbf{CNN NPU Overlay \& Compiler (Capstone):}
Designed a \textbf{VLIW-based Python compiler} packing 130-bit instruction chains with dependency tracking and NOP insertion;
engineered a SystemVerilog RTL scheduler with \textbf{credit-based flow control}, achieving \textbf{450\,MHz Fmax} on Intel Stratix~10~NX.}
}
\itemListEnd
\vspace{-2.5pt}
\projCategory{Error-Correcting Codes \& Graphical Inference}

\itemListStart
\small{
\myItem{\textbf{Graph-Based Error-Correcting Codes:}
Implemented \textbf{LDPC, Polar, and Fountain/LT} encoders/decoders over erasure channels, with custom simulators in Julia and MATLAB.
\href{https://github.com/fireflyndmoon43/ECE1508-Graphs-Codes-and-Inference}{\textcolor{NavySecondary}{\textbf{[Code]}}}}

\myItem{\textbf{Error Control Coding:}
Implemented \textbf{convolutional} and \textbf{BCH} codes with Viterbi decoding and finite-field arithmetic over \(GF(2^m)\).}
}
\itemListEnd

\vspace{-2.5pt}

% ---------- Awards + Skills ----------
\vspace{-2pt}
\noindent
\begin{minipage}[t]{0.46\textwidth}
  \cvsection{Awards \& Talks}
  \vspace{-6pt}
  \itemListStart
  \footnotesize{
    \item Edward S. Rogers Sr. Dept. Betz Entrance Scholarship (\$5,000) \hfill \textit{2017}
    \item Certificate in Engineering Business \hfill \textit{Jun.~2022}
    \item Qualcomm Panel: \textit{Demystifying Machine Learning} \hfill \textit{Mar.~2025}
  }
  \itemListEnd
\end{minipage}
\hfill
\begin{minipage}[t]{0.52\textwidth}
  \cvsection{Technical Skills}
  \vspace{-6pt}
  \begin{itemize}[leftmargin=0pt, label={}]
    \footnotesize{
      \item \textbf{Software \& Tools:}
      C/C++, Python (NumPy/Keras), Julia, SystemVerilog, SIMD, MLIR/LLVM,
      ISA simulation, Graph IR, Git, Jenkins CI/CD, Quartus Prime,
      Cadence Virtuoso, Synopsys VCS
    }
  \end{itemize}
\end{minipage}


\end{document}
